\section{Model Establishment}

\subsection{Supplier Evaluation}

Each supplier receives a weighted score based on normalized price advantage, transport retention, and reliability:

\begin{equation}
S_i = 0.35 P_i + 0.30(1-\ell_i) + 0.35 R_i,
\end{equation}

where $P_i$ is a normalized inverse-price score, $\ell_i$ is the loss rate, and $R_i$ is the reliability score. The weights are illustrative and should be replaced by entropy weighting, AHP, or a justified expert rule in a real study.

The score has three roles in the v1.0 pipeline. First, it converts heterogeneous indicators into a single decision signal. Second, it creates a traceable bridge from data processing to supplier selection. Third, it gives the paper a natural place to discuss weighting risk, which is important for later quality checking. A generated paper should not simply name TOPSIS or AHP; it should explain how the indicator table actually affects the downstream decision.

\subsection{Ordering Baseline}

For each week, the required delivered amount is:

\begin{equation}
D_t^{req} = \max(0, d_t + 15 - I_{t-1}),
\end{equation}

where 15 is the safety inventory target. Suppliers are considered in descending evaluation score. The ordered quantity is limited by supplier capacity and adjusted by transport loss:

\begin{equation}
I_t = I_{t-1} + \sum_i q_{i,t}(1-\ell_i) - d_t.
\end{equation}

This is a greedy baseline, not a globally optimal mixed-integer planning model. It is sufficient for v1.0 pipeline verification.

\subsection{Extension to a Full Optimization Model}

The greedy rule can be replaced by a mixed-integer planning model when the paper needs stronger mathematical depth. Let $q_{i,t}$ denote the order quantity from supplier $i$ in week $t$, and let $I_t$ denote ending inventory. A full model can minimize total procurement cost:

\begin{equation}
\min \sum_t \sum_i c_i q_{i,t},
\end{equation}

subject to inventory balance, capacity limits, safety inventory, and non-negativity:

\begin{align}
I_t &= I_{t-1} + \sum_i q_{i,t}(1-\ell_i) - d_t,\\
0 &\le q_{i,t} \le C_i,\\
I_t &\ge I^{safe}.
\end{align}

This formulation is not solved in the demo because the goal here is a low-dependency closed-loop test. However, writing it into the paper skeleton is useful: it shows where a future exact solver, integer decision variables, transport-provider coupling, and robustness constraints will fit.

\subsection{Validation Targets}

The model is checked against three targets:

\begin{enumerate}
\item feasibility: ending inventory should not fall below the safety threshold;
\item economy: weekly and total cost should be visible and explainable;
\item robustness: changes in transport loss should not invalidate the basic plan without being detected.
\end{enumerate}

These targets determine the figures and tables in the results section. This is the intended v1.0 pattern: model equations should predict what evidence the paper must display.
