\section{Strengths, Limitations, and Extensions}

The v1.0 demo has four strengths. First, it connects forecasting to production decisions instead of ending at a descriptive time-series result. Second, it generates reproducible tables and figures rather than manually describing results. Third, it records outputs in stable locations for later review. Fourth, it exposes both a feasible high-capacity reference case and a stressed low-capacity case, which is structurally closer to an actual production-route E paper.

The limitations are also clear. The data are synthetic, the planning algorithm is greedy, the forecast rule is intentionally lightweight, and demand uncertainty is only represented through the scenario comparison. The current model does not include order lead time, minimum batch size, supplier disruption, carrier allocation, or multi-material coupling. Therefore the result should be read as a workflow demonstration, not as an operational recommendation.

A stronger version should use real demand history, richer forecast candidates, mixed-integer programming, capacity-sharing constraints, and scenario stress tests. It should also include more contest-style evidence: perturbation experiments, constraint violation audits, comparison against an exact or heuristic baseline, and an appendix that lists code files and output paths.

For the larger project, this demo suggests a practical development rule. Each future problem type should have a small closed-loop route before the repository attempts broad automation. For example, the classification route should produce preprocessing tables, feature plots, confusion matrices, and error analysis; the geometry route should produce diagrams, coordinate tables, and residual plots; the planning route should produce decision tables, feasibility checks, and sensitivity curves.
